Differentiation with respect to weights for a `hyper3` object

### 2024-05-28 inst/grad_weight.Rmd
a more exacting example

>>>>

Come to think of it, all the `wanted` arguments are the same length
(two).  A more exacting test would be:

$$
\frac{(p_1)^3\,(w p_2)^4}{(p_1+wp_2)^7}\cdot
\frac{p_2^5\,(wp_1+wp_3)^2}{(wp_1+p_2+wp_3)^7}
$$

```{r label=moreexacting}
m <- function(w){
  H <- hyper3()
  H[c(p1=1)] <- 3
  H[c(p2=w)] <- 4
  H[c(p1=1,p2=w)] <- -7
  H[c(p2=1)] <- 5
  H[c(p1=w,p3=w)] <- 2
  H[c(p1=w,p2=1,p3=w)] <- -7
  H
}
w <- 1.888
dw <- 1e-4
probs <- c(p1=0.4,p2=0.1, p3=0.5)
m(w)

H <- m(w)
loglik(probs,H)

diffD <- (
 grad_weight_single(H, probs, c(p2=w          ), "p2"        ) +
 grad_weight_single(H, probs, c(p1=1,p2=w     ), "p2"        ) +
 grad_weight_single(H, probs, c(p1=w,p3=w     ), c("p1","p3")) +
 grad_weight_single(H, probs, c(p1=w,p2=1,p3=w), c("p1","p3"))
 )

LHS <- (loglik(probs,m(w+dw/2)) -loglik(probs,m(w-dw/2)))/dw
RHS <- diffD
c(LHS,RHS,LHS-RHS)
```
